A finite-state morphological transducer for Kyrgyz

### 2011-10-14 dev/paper/paper.tex
moar fixes

@@

>>>>

% for glosses
\newcommand{\eng}[1]{`{\em #1}'}
%dammit, sc doesn't seem to be working
\newcommand{\gmk}[1]{\textsc{#1}}

@@

\begin{table}[htbp]
	\caption{examples comparing voicing and devoicing in Kyrgyz}\label{exvoicing}
	\subtable{
		\begin{tabular}{lll}
			\toprule
			underlying & surface & gloss \\
			\midrule
			/алма-DA/ & [алмада] & \eng{apple--\gmk{LOC}} \\
			/каз-DA/ & [казда] & \eng{goose--\gmk{LOC}} \\
			/баш-DA/ & [башта] & \eng{head--\gmk{LOC}} \\
			\bottomrule
		\end{tabular}
	}
	\hspace{2em}
	\subtable{
		\begin{tabular}{lll}
			\toprule
			underlying & surface & gloss \\
			\midrule
			/алма-GA/ & [алмага] & \eng{apple--\gmk{DAT}} \\
			/каз-GA/ & [казга] & \eng{goose--\gmk{DAT}} \\
			/баш-GA/ & [башка] & \eng{head--\gmk{DAT}} \\
			\bottomrule
		\end{tabular}
	}
\end{table}

Here, the underlying /D/ is always realised as [д] when after a voiced segment (including a vowel), but is realised as [т] after an unvoiced consonant, while underlying /G/ is always realised as [г]\footnote{‹г› is pronounced [ɣ] in the context of front vowels and [ʁ] in the context of back vowels; it also has realisations of [ɡ] and [ɢ] after nasals.} after a voiced segment, but is realised as [к]\footnote{‹к› is realised as [q] in the context of back vowels and [k] in the presence of front vowels.} after voiceless consonants.
